### 2023-03-27 main/chapter_2ljets.tex
cr/vr/sr usage in fits and decision metrics

\FloatBarrier
\section{Design}
\label{sec:2ljets_design}
Perhaps the most impactful decision in an \atlas\ SUSY search is the design of
its regions.
Like most decisions, these designs must be made to balance conflicting and
vaguely-specified desires, and are informed with incomplete information.

>>>>

\FloatBarrier
\section{Design}
\label{sec:2ljets_design}
Perhaps the most impactful decision in an \atlas\ SUSY search is the design of
its regions.
Like most decisions, these designs must be made to balance conflicting and
vaguely-specified desires, and are informed with incomplete information.
When designing the regions described in this section, I conducted a manual
search and optimization with human feedback from the $\twoljets$ team.
Expected significance statistics were used to assess the sensitivity of a
region design to particular representative signals, but final decisions were
made to maximise the extend of projected exclusion contours as evaluated by our
statistical software.

### 2023-03-27 main/chapter_searches.tex
cr/vr/sr usage in fits and decision metrics

Our searches see data only through discrete histogram bins named `regions',
which are defined by logical selections in event variables.
To communicate their intended uses, we further categorize these bins into
`control', `validation', and `signal' regions;
Figure~\ref{fig:searches_histfitter_regions} illustrates the uses of these
three region types.

@@

Various fits are useful to extract different results from search regions.
We briefly describe the three classes of fit here, and shall see examples
of their results in Chapter~\ref{chapter:2ljets}.

@@

\paragraph{Exclusion fits.}
Model-dependent `exclusion' fits add simulated yields from precisely
defined models to the \heplikelihood\ model.
These fits can use multiple signal regions simultaneously, and couple the
effect of parametrized modifications to the signals and backgrounds between
the bins of those regions.

>>>>

Our searches see data only through discrete histogram bins named `regions',
which are defined by logical selections in event variables.
Each search has its own desiderata, so many different criteria can be used
to choose these logical selections; broadly, however, selections are made to
separate signals from backgrounds, such that data appearing in the regions are
informative as to whether signals are present and what the values of unknown
parameters might best explain the data.
To communicate their intended uses, we further categorize these bins into
`control', `validation', and `signal' regions;
Figure~\ref{fig:searches_histfitter_regions} illustrates the uses of these
three region types.

@@

Various fits are useful to extract different results from search regions.
We briefly describe the three classes of fit here, and shall see examples
of their results in Chapter~\ref{chapter:2ljets}.
Control regions are included in all fits with an intent to constrain the
normalization of Standard Model background samples.
Validation regions are not directly included as likelihood constraints in any
fits, but are used for visual inspection only, such that the analysts can
iteratively adapt their modelling to look good in validation regions without
directly biasing final results.
Signal regions are included only once the backgrounds are constrained and
validated and only in fits where one is testing for the presence of signals
as detailed below.

@@

\paragraph{Exclusion fits.}
Model-dependent `exclusion' fits add simulated yields from precisely
defined models to the \heplikelihood\ model.
These fits can use multiple signal regions and control regions simultaneously,
and couple the effect of parametrized modifications to the signals and
backgrounds between the bins of those regions.
